---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# circulaR

<!-- badges: start -->
<!-- badges: end -->

The goal of circulaR is to identify and annotate circular RNA (circRNA) contents from total RNA sequencing data. The package contains functionality for importing chimeric read data generated with the STAR aligner [link: Alexander Dobin - STAR github], filtering backsplice junctions, and overlapping known gene models with the identified backsplice junctions.

## Installation

### Software
In order to use the tools provided in this guide, and to install the required dependencies, the following external software must be installed:

 * libgit2: [Ubuntu 20.04 LTS](https://packages.ubuntu.com/source/focal/libgit2) [Arch Linux](https://archlinux.org/packages/extra/x86_64/libgit2), [Mac Homebrew](https://formulae.brew.sh/formula/libgit2)
 * gcc-fortran: [Ubuntu 20.04 LTS](https://packages.ubuntu.com/focal/gfortran)  [Arch Linux](https://archlinux.org/packages/core/x86_64/gcc-fortran) [Mac installation instructions](https://gcc.gnu.org/wiki/GFortranBinariesMacOS)
 * R: [Ubuntu](https://cran.r-project.org/bin/linux/ubuntu/) [Arch linux] (https://archlinux.org/packages/extra/x86_64/r/) [Mac](https://cran.r-project.org/)
 * RStudio: [Ubuntu & Mac](https://rstudio.com/products/rstudio/download/) [Arch linux](https://aur.archlinux.org/packages/rstudio-desktop-bin/)

### R packages
In order to install the `circulaR` R package, you must ensure to install the following Biocodncutor packages:

 * AnnotationDbi
 * BiocGenerics
 * BSgenome
 * DESeq2
 * ensembldb
 * GenomeInfoDb
 * GenomicFeatures
 * GenomicRanges
 * Gviz
 * IRanges
 * Rsamtools
 * S4Vectors
 
```{r, eval=FALSE}
install.packages("BiocManager")
BiocManager::install(c("AnnotationDbi", "BiocGenerics", "BSgenome", "DESeq2", "ensembldb", "GenomeInfoDb", "GenomicFeatures", "GenomicRanges", "Gviz", "IRanges", "Rsamtools", "S4Vectors"))
```

In addition, `devtools` r package must be installed, to enable easy installation of `circulaR` from github.
```{r, eval=FALSE}
install.packages("devtools", dependencies = TRUE)
devtools::install_github("https://github.com/KasperThystrup/circulaR")
```

#### Trobuleshooting
This should install all dependencies from the official CRAN repository. However, if something does not work out, try to install the CRAN dependencies manually before running the install_github command again:

 * dplyr
 * ggplot2
 * parallel
 * pbmcapply
 * plyr
 * readr
 * RSQLite
 * stringi
 * tibble
 * tidyr
 * Hmisc

```{r, eval=FALSE}
install.packages(c("dplyr", "ggplot2", "parallel", "pbmcapply", "plyr", "readr", "RSQLite", "stringi", "tibble", "tidyr", "Hmisc"))
devtools::install_github("https://github.com/KasperThystrup/circulaR")
```
